---
title: "Cancer Drug Classifications"
author: "Meera Y. Patel, M.D."
output: 
  html_document:
    theme: flatly
    highlight: kate  
    toc: yes
    number_sections: true
    toc_depth: 3 
    toc_float: 
      collapsed: false  
      smooth_scroll: false
    code_folding: show #or hide
    df_print: paged
    fig_height: 5 
    fig_width: 7 
    fig_caption: true
    dev: png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      cache = FALSE,
                      cache.path = "cache/",
                      child = NULL, #file/s to knit and then include,
                      collapse = FALSE, #collapse all output into a single block,
                      error = TRUE, #display error messages in doc. FALSE stops render when error is thrown
                      fig.align = "center", #left, right, center, or default
                      include = TRUE, #include chunk?
                      message = TRUE, #display code messages?
                      tidy = TRUE, #tidy code 
                      warning = TRUE, #include warnings?
                      results = "markup"
                        # "asis": passthrough results
                        # "hide": do not display results 
                        # "hold": put all results below all code
                      )
```
  
Last updated: `r Sys.Date()`  
  
## Introduction  

Drug Classification Challenges:  

- Clinically relevant classification for data collection and analysis purposes   
- Interoperability across consortia, including ASCO   




## Reingold-Tilford Tree Diagrams  

### Antibody Drug Conjugates  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_ANTIBODY_DRUG_CONJUGATE_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_ANTIBODY_DRUG_CONJUGATE_with_siblings.html')
```



### Cellular Therapy  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/CELLULAR_THERAPY_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/CELLULAR_THERAPY_with_siblings.html')
```



### Checkpoint Inhibitors  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_CHECKPOINT_INHIBITOR_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_CHECKPOINT_INHIBITOR_with_siblings.html')
```



### Cytotoxic Chemotherapy  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/CYTOTOXIC_CHEMOTHERAPY_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/CYTOTOXIC_CHEMOTHERAPY_with_siblings.html')
```



### Endocrine Therapy  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/ENDOCRINE_THERAPY_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/ENDOCRINE_THERAPY_with_siblings.html')
```



### Immunomodulators and Immunostimulants  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_IMMUNOMODULATOR_AND_IMMUNOSTIMULANTS_EXCLUDING_IMMUNOSUPPRESSANTS_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_IMMUNOMODULATOR_AND_IMMUNOSTIMULANTS_EXCLUDING_IMMUNOSUPPRESSANTS_with_siblings.html')
```



### Intravesicular Therapy  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/INTRAVESICULAR_THERAPY_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/INTRAVESICULAR_THERAPY_with_siblings.html')
```



### Monoclonal Antibody Targeted Therapy  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_MONOCLONAL_ANTIBODY_TARGETED_THERAPY_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_MONOCLONAL_ANTIBODY_TARGETED_THERAPY_with_siblings.html')
```



### Other Immunotherapy  


#### Without Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_OTHER_without_siblings_2_to_2.html')
```



#### With Siblings  

```{r,echo=FALSE}
htmltools::includeHTML('widgets/IMMUNOTHERAPY_OTHER_with_siblings.html')
```

