---
title: "Analysis of Takeda's Studies in the AACT Database"
author: "Meera Y. Patel, M.D."
date: "`r Sys.Date()`"
output: 
  html_document:
    css: style.css
    theme: flatly
    highlight: kate  
    toc: yes
    number_sections: true
    toc_depth: 3 
    toc_float: 
      collapsed: false  
      smooth_scroll: false
    code_folding: show #or hide
    df_print: paged
    fig_height: 5 
    fig_width: 7 
    fig_caption: true
    dev: png
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "##",
                      tidy = TRUE, #`styler` to use styler:style_text() to reformat code
                      tidy.opts = list(blank = FALSE, width.cutoff = 60),
                      echo = TRUE,
                      eval = TRUE,
                      cache = TRUE,
                      cache.path = "reports/cache/",
                      child = NULL, #file/s to knit and then include,
                      collapse = FALSE, #collapse all output into a single block,
                      error = TRUE, #display error messages in doc. FALSE stops render when error is thrown
                      fig.align = "center", #left, right, center, or default
                      fig.width = 7, #inches
                      fig.height = 7, #inches
                      fig.asp=0.50, #adds whitespace around images
                      include = TRUE, #include chunk?
                      message = FALSE, #display code messages?
                      tidy = TRUE, #tidy code 
                      warning = FALSE, #include warnings?
                      results = "markup"
                        # "asis": passthrough results
                        # "hide": do not display results 
                        # "hold": put all results below all code
                      )
```

The AACT database available through ClinicalTrials.gov is used 
for this analysis. Version 2021-01-17 is used for this analysis.  

```{r,results='hide'}
library(tidyverse)
library(pg13)
library(ggplot2)
```

Clinical Trials associated with Takeda are queried by 
searching for the phrase “Takeda” in the "acronym", "brief_title",
"official_title", "source", "limitations_and_caveats", "why_stopped", 
"ipd_access_criteria", "ipd_url", and "plan_to_share_ipd_description" 
fields in the CTGOV.STUDIES Table.  

```{r,results='hide'}
conn <- local_connect("aact")

studies_fields <-
ls_fields(conn = conn,
          schema = "ctgov",
          table = "studies")

takeda_studies <- list()
for (i in seq_along(studies_fields)) {
  studies_field <- studies_fields[i]
  sql_statement <-
  SqlRender::render(
    "SELECT *
    FROM ctgov.studies s
    WHERE LOWER(s.@studies_field::varchar) LIKE LOWER('%Takeda%')",
    studies_field = studies_field
  )
  takeda_studies[[i]] <-
    query(conn = conn,
          sql_statement = sql_statement)
  names(takeda_studies)[i] <- studies_field
}

dc(conn = conn)

takeda_studies2 <-
  takeda_studies %>%
  bind_rows() %>%
  distinct()
```

The "overall_status" describes the stage of a trial's execution 
and provides a glimpse into the overall clinical trial activity 
at Takeda.  

```{r}
ggplot(data =
         takeda_studies2 %>%
           count(overall_status) %>%
           rename(`Overall Status` = overall_status,
                  Count = n),
      mapping = aes(x = `Overall Status`,
                    y = Count,
                    fill = `Overall Status`,
                    label = Count)) +
  geom_col() +
  theme_minimal() +
  labs(title = "Takeda Studies Across all Phases") +
  scale_fill_brewer(palette = "Paired") +
  theme(axis.text.x = element_blank()) +
  geom_text(aes(label=Count), vjust=-0.2, color="black", size=3.5)
```

“Active Statuses” are statuses that are potential targets 
for ongoing data cleaning efforts before the study is closed 
and the database is locked. Here, it is arbitrarily defined 
as those with overall status of “Active, not recruiting”, 
“Available”, and “Recruiting”.  

The total actual or anticipated enrollment 
is calculated For all studies that are active according to the 
definition above. This calculation gives an idea of the total 
number of patients that are covered by a data visualization 
tool like Platypus.  

```{r}
active_statuses <- c("Active, not recruiting",
                     "Available",
                     "Recruiting")

takeda_studies3 <-
  takeda_studies2 %>%
  filter(overall_status %in% active_statuses)

ggplot(data =
         takeda_studies3 %>%
         filter(!is.na(enrollment_type)) %>%
         group_by(enrollment_type) %>%
         summarize(total = sum(enrollment)) %>%
         rename(`Enrollment Type` = enrollment_type,
                `Total` = total),
       mapping = aes(x = `Enrollment Type`,
                     y = Total,
                     fill = `Enrollment Type`,
                     label = Total)) +
  geom_col() +
  theme_minimal() +
  labs(title = "Takeda Active Studies Enrollment") +
  scale_fill_brewer(palette = "Paired") +
  theme(axis.text.x = element_blank()) +
  geom_text(aes(label=Total), vjust=-0.2, color="black", size=3.5)
```

Since each study can be in various phases, which would require 
different degree of medical review, the active studies are further 
broken down by phase. Non-interventional studies are summarized 
by subtypes “Observational”, "Observational [Patient Registry]",
and “Expanded Access”.

```{r}
takeda_studies4 <-
  takeda_studies3 %>%
  mutate(phase = coalesce(phase, study_type)) %>%
  mutate(phase = factor(phase,
                        levels = c("Phase 1",
                                   "Phase 1/Phase 2",
                                   "Phase 2",
                                   "Phase 2/Phase 3",
                                   "Phase 3",
                                   "Phase 4",
                                   "Observational",
                                   "Observational [Patient Registry]",
                                   "Expanded Access"))) %>%
  mutate(study_type = factor(study_type,
                             levels =
                               c("Interventional",
                                 "Observational",
                                 "Observational [Patient Registry]",
                                 "Expanded Access")))

ggplot(data =
         takeda_studies4 %>%
         group_by(phase) %>%
         mutate(n = length(phase)) %>%
         ungroup() %>%
         distinct(Phase = phase,
                Count = n,
                `Study Type` = study_type),
       mapping = aes(x = Phase,
                     y = Count,
                     fill = `Study Type`,
                     label = Count)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Takeda Active Studies by Study Type and Phase") +
  scale_fill_brewer(palette = "Paired") +
  theme(axis.text.x = element_text(angle = 30, size = 5)) +
  geom_text(color="black", size=3.5, vjust=-0.1)
```

Since each new study could mean a new Platypus project, the 
total number of new studies by year, grouped by phase, are calculated.  

```{r}
ggplot(data =
         takeda_studies4 %>%
         rubix::filter_at_grepl(col = phase,
                                grepl_phrase = "Phase",
                                ignore.case = FALSE) %>%
         mutate(start_year = lubridate::year(start_date)) %>%
         group_by(phase,start_year) %>%
         mutate(n = length(phase)) %>%
         ungroup() %>%
         distinct(Phase = phase,
                `Start Year` = start_year,
                Count = n),
       mapping = aes(x = `Start Year`,
                     y = Count,
                     fill = Phase,
                     label = Count)) +
  geom_col() +
  theme_minimal() +
  labs(title = "Takeda New Active Investigational Studies by Year") +
  scale_fill_brewer(palette = "Paired") +
  theme(axis.text.x = element_text(angle = 30),
        legend.position = "bottom") +
  geom_text(size = 2, 
            position = position_stack(vjust = 0.5))
```

Conversely, each completed study could mean either a bump in 
workload (activities to close a database) and/or a removal of 
a project from the Platypus portfolio. The number of completed 
studies by year, grouped by phase, is calculated.  

```{r}
ggplot(data =
         takeda_studies2 %>%
         rubix::filter_at_grepl(col = phase,
                                grepl_phrase = "Phase",
                                ignore.case = FALSE) %>%
         filter(overall_status %in% c("Completed")) %>%
         mutate(completion_year = lubridate::year(completion_date)) %>%
         group_by(phase,completion_year) %>%
         mutate(n = length(phase)) %>%
         ungroup() %>%
         distinct(Phase = phase,
                `Completion Year` = completion_year,
                Count = n),
       mapping = aes(x = `Completion Year`,
                     y = Count,
                     fill = Phase,
                     label = Count)) +
  geom_col() +
  theme_minimal() +
  labs(title = "Takeda Completed Investigational Studies by Year") +
  scale_fill_brewer(palette = "Paired") +
  theme(axis.text.x = element_text(angle = 30),
        legend.position = "bottom")  +
  geom_text(size = 2, 
            position = position_stack(vjust = 0.5))
```

I also want to see the distribution of study length from start to completion by phase. This would translate into the length of time a given study would be in the Platypus portfolio as it is being monitored for medical review.
